Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-10-31 paper/galsize_paper.tex
Increased figure size
Updated abstract

\begin{abstract}
We place empirical constraints on the connection between dark matter halos and galaxy half-light radii, $\rhalf.$ Using the SDSS, we show that smaller galaxies cluster much more strongly than larger galaxies at fixed stellar mass.  Using Halotools to forward-model the observations, we find that the clustering signal generically requires satellite galaxies to be smaller than central galaxies of the same halo mass.  We present a simple empirical model consistent with the clustering results, in which galaxy size is proportional to halo virial radius at the time of peak halo mass, and the scatter is strongly correlated with halo scale radius.  Models in which galaxy size is related to stellar mass only or that have uncorrelated scatter in galaxy size both fail the clustering test, even considering effects of satellite stripping and orphan galaxies.  These results suggest that the relative size of centrals and satellites is predetermined at the time of satellite infall, and supports the notion that $L_\ast$ galaxy and halo profiles co-evolve across many Gyr of cosmic time.
\end{abstract}

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/penultimate_clustering_ratios_no_orphans.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering.}
Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj.$ We define a galaxy as ``large" or ``small" according to whether it is above or below the median size for its stellar mass, so that in each panel, the stellar mass functions of the ``large" and ``small" subsamples are identical, as described in the text. The y-axis shows {\em clustering strength ratios,} so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass. Each panel shows results separately for different volume-limited $\mstar-$threshold samples; predictions of three different models are shown in each panel. See \S\ref{subsec:model} for a description of each model.}
\label{fig:clustering_ratio_upshot}
\end{figure}
%-----------------------------------------------------------------------------------------------------

>>>>

\begin{abstract}
We place empirical constraints on the connection between dark matter halos and galaxy half-light radii, $\rhalf.$ Low-redshift SDSS measurements show that smaller galaxies cluster much more strongly than larger galaxies at fixed stellar mass. Using {\tt Halotools} to forward model the observations, we find that the clustering signal generically requires satellite galaxies to be smaller than central galaxies of the same halo mass. We present a simple empirical model consistent with the clustering results, in which galaxy size is proportional to halo virial radius at the time of peak halo mass. We use this model to predict how galaxy lensing, $\Delta\Sigma,$ should depend on $\rhalf$ for $\mstar-$complete galaxy samples. Other simple empirical models fail the clustering test, such as models in which galaxy size is related to stellar mass alone, and models that treat splashback galaxies as ordinary centrals; these failures persist even when accounting for possible effects from satellite stripping and orphan galaxies. Our results suggest that the relative size of centrals and satellites is predetermined at the time of satellite infall, and that a remarkably simple scaling relation emerges from the complex physics regulating galaxy size. 
%We make our python code publicly available to support ongoing efforts to generate realistic synthetic galaxy catalogs for large cosmological surveys.  
\end{abstract}

@@

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=12cm]{FIGS/penultimate_clustering_ratios_no_orphans.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering.}
Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj.$ We define a galaxy as ``large" or ``small" according to whether it is above or below the median size for its stellar mass, so that in each panel, the stellar mass functions of the ``large" and ``small" subsamples are identical, as described in the text. The y-axis shows {\em clustering strength ratios,} so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass. Each panel shows results separately for different volume-limited $\mstar-$threshold samples; predictions of three different models are shown in each panel. See \S\ref{subsec:model} for a description of each model.}
\label{fig:clustering_ratio_upshot}
\end{figure*}
%-----------------------------------------------------------------------------------------------------
